Vragenlijst thesis evaluatie

### 2015-08-19 doc/template/chap-9.tex
veranderingen opslagen

\chapter{FlipIt with propagation delay}
\label{chapter2:FlipIt with virus propagation}
%\documentclass[10pt]{article}
%\begin{document}

@@

\section{Difference between FlipIt with and without propagation delay}
\label{ch2:diffFlip}

@@

In chapter \ref{chapter4: Worm propagation}, when discussing future work, the use of a matrix model is discussed to determine the probability that a node is infected by malware.  \\
The attacker only has one action: sending different kinds of malware to a computer network. Every time the attacker flips the resource, he does this by sending a new kind of malware e.g worm to the system. The attacker does not send the same malware again, because if the computers are patched, the malware will be unable to penetrate the system. The node can be a targeted node or a random node. If the attacker has knowledge about the topology of the network, the attacker can choose to target a specific node. Most likely, this will be the node that can infect all other nodes in a minimum timespan.

@@

In this paper we assume that both moves of the attacker and the defender are stealthy. Our motivation for a defender with stealthy moves is that it can not be assumed that every attacker can receive feedback from an APT. Some APTs can be resident on a isolated network (e.g. the Stuxnetworm), meaning that there is no way to connect to the Internet. \\

@@

Even when the APT is launched to steal sensitive information the defender can set-up a honey pot, making the attacker believe that he is stealing sensitive information, but the information in the honeypot is all fake. Honeypots emulate services or creates multiple instances of real operating systems and can pretend to have sensitive information.  The case where the moves of the defender are non stealthy has already been investigated by Laszka \citep{MitigationNonTargeted}.

@@

\textbf{No feedback (non-adaptive)}\\
Non-adaptive strategies are chosen because of the assumption that both players will receive no feedback during the game. This is motivated by the fact that the identity of the attackers and their attack strategy is rarely known to the defenders. In the case of the attacker, if an attacker wants to have feedback it may be disadvantageous if he wants to stay undetected. If the attacker wants to have feedback, the malware needs to make a connection with the attacker to provide this feedback. For example, this can cause more network traffic for the defender to detect. \\

@@

\section{Formalization of the periodic game with propagation delay}
\label{ch2:periodicvirus}

@@

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.7]{Images/DefFlip.pdf}
\caption{Formalization of a FlipIt game with delay: A representation of a FlipIt game where both players are playing periodically. Every move or flip is indicated by a green or orange circle, respectively dark gray and light grey.  The defender is represented in green (dark grey) and plays with a period of $\delta_{D}$. The flip of the attacker is represented by a white circle, but because there is a delay d, the attacker only controls the resource after time d represented by an orange circle (light grey). The attacker plays with a period of $\delta_{A}$. The green and orange rectangles represent the amount of time the respective player is in control of the resource.}
\label{FlipItDelay}
\end{figure}

\begin{description}
\item $i$: Denotes the player. \textit{D} denotes the defender, and \textit{A} denotes the attacker which differs form the notation in \citep{FlipIt}, where the defender is denoted by the subscript \textit{0} and the attacker by the subscript \textit{1}.
\item $\delta_{i}$: The length of the interval between two consecutive moves of player \textit{i}. 
\item $\alpha_{i}$: The average flip rate of player \textit{i}, given by $\alpha_{i}=1/\delta_{i}$.
\item $k_{i}$: The cost of player \textit{i}'s moves.
\item $d$: The delay caused by the virus propagation.
\item $G_{i}(t)$: The total gain of player \textit{i}, which is the amount of time player \textit{i} is in control over the resource up to time \textit{t}.
\item $\gamma_{i}$: The average gain rate of player \textit{i}, defined as $G_{i}(t)/t$
\item $\beta_{i}$:  The average benefit rate up to time \textit{t}, defined as  $\beta_{i} = \gamma_{i} -k_{i} \alpha_{i} $.
\item $opt_{i}$: The optimum function for player \textit{i}. 
\end{description}

The adaptation of the FlipIt model starts from the assumption that, when an attacker attacks at time \textit{t}, he doesn't get immediate control over the resource, but he only gains control at time \textit{t + d}, with $d$ denoting the time needed to infect a sufficient number of (or all) nodes. If the defender flips the network before the period $d$ has elapsed (so, somewhere between $t$ and $t + d$), then the attacker will never gain full control over the resource. (See figure \ref{dt} at point 3 and 4). This implies that the mathematical formulas for gain and benefit need to be adapted to the fact that the attacker loses part of his benefit because of this delay. In the remainder of this paper, we will adapt the formalization of the FlipIt game using the delay variable $d$. \\

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.7]{Images/Delayuitgelegd.pdf}
\caption{The first game is the basic FlipIt game. The second is the FlipIt game with a delay. During the first flip of the attacker, the defender moves after the delay (point 2), resulting in the attacker gaining control over the resource, until the defender flips. During the second flip of the attacker, the defender flips at time t+d, causing the defender to retain control over the resource before the attacker. During the third and final flip of the attacker, the defender flips during time t+d, causing the attacker to never gain control over the resource. }
\label{dt}
\end{figure}

%
We split the formalization in three cases. Similarly as in \cite{FlipIt}, there is the case where the defender plays at least as fast as the attacker, and the case where the attacker plays at least as fast as the defender. For each of these cases, the benefit formula of the basic case without delay is presented first, and subsequently the delay is introduced.  The third case is a special case where the period of the defender is smaller than the delay.\\

In the original model of FlipIt \cite{FlipIt}, the authors express the formulas in terms of $\alpha_{D}$ and $\alpha_{A}$. However, when introducing the delay, some formulas become much simpler when expressed in terms of $\delta_{D}$ and $\delta_{A}$. Therefore in the remainder of this paper, we will formulate the model using both $\alpha_{i}$ and $\delta_{i}$, depending on which variable gives the simplest representation of the formulas.

@@

This however results in an overestimation. 
%By simulation the game, it can be notices that the closer $\delta_{A}/\delta_{D}$ is equal to one, the better the approximation. If $\delta_{A}/\delta_{D} = 1$ the result is correct. 
The reason this formula overestimates the benefit of the attacker is that it assumes that the defender is always in control during the delay. However, if the attacker was in control in the previous interval, then he continues to be in control during the period of the delay, see figure \ref{fig:case2} situation 5 to 7. This means that the average benefit formulas for this case cannot be derived from one interval only; what happens in the previous interval must be taken into account. \\

@@

Consider a timespan $\delta_{A} + d$, representing the attacker's interval followed by the delay period in his next interval. If we assume that $\delta_{A}+d<\delta_{D}$, we can infer that the defender will never move twice during this timespan.
Because $d + \delta_{A} \leq \delta_{D}$ the next move of the defender in this second interval will never occur during the delay, meaning that the entire delay can be considered as an extra benefit resulting of a play in the previous interval. 
So, every time the defender plays, he will get an average gain of $\dfrac{\delta_{A}}{2}$ in the interval where he plays and in the next interval will always receive a extra gain of $d$, yielding a total average gain per interval of
$\dfrac{(d+\dfrac{\delta_{A}}{2})}{\delta_{A}}$

For the remainder of the analyses we consider two cases, Case a and Case b, depending on whether the delay is shorter or longer than the difference between the attacker's and the defender's period.  \\

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.7]{../../doc/template/Images/FlipIt2.pdf}
\caption{All possible cases for the attacker and the defender in Case 2.A where $d + \delta_{A} < \delta_{D}$. As can be seen in cases (1) to (4), the defender will have control during a period of \textit{d} over the resource in the next interval when the defender has flipped in the previous interval.}
\label{fig:case2}
\end{figure}

@@

It is crucial that $ \delta_{D}$ is at least as large as $d + \delta_{A}$. If not, the defender can move during the delay in the interval following the interval in which the defender already moved. This would result in an overlap between the average gain of $\dfrac{\delta_{A}}{2} +d$ and the delay. The above benefit formula would then include too much gain for the defender: the potential overlap during the delay would be counted twice. See figure \ref{countedtwice}\\

@@

We calculated the benefit for three cases: when $\delta_{D}$ is smaller than $d$. When $\delta_{A}$ is smaller than $\delta_{A}$ and when it is larger than $\delta_{A}$.
The benefit formulas of case 1 and case 2.b result in the same formula. Consequently, these two formulas can be brought together by adapting the border conditions. The first figure in figure \ref{Borders} shows all the cases and it can be seen that the border condition of case 1 and case 2.b can be brought together. This can be seen as the second figure in \ref{endborders}. \\

>>>>

\chapter{FlipIt with Propagation Delay}
\label{chapter2:FlipIt with virus propagation}
%\documentclass[10pt]{article}
%\begin{document}

@@

\section{Difference between FlipIt with and without Propagation Delay}
\label{ch2:diffFlip}

@@

In chapter \ref{chapter4: Worm propagation}, when discussing future work, the use of a matrix model is discussed to determine the probability that a node is infected by malware. A practical example of a flip of the defender may consist of patching, formatting, disk-wiping or unplugging a computer on the network. \\
The attacker only has one action: sending different kinds of malware to a computer network. Every time the attacker flips the resource, he does this by sending a new kind of malware e.g virus to the system. The attacker does not send the same malware again, because if the action of the defender, e.g. consists of patching, the malware will be unable to penetrate the system. The node can be a targeted node or a random node. If the attacker has knowledge about the topology of the network, the attacker can choose to target a specific node. Most likely, this will be the node that can infect all other nodes in a minimum timespan.

@@

In this paper we assume that both moves of the attacker and the defender are stealthy. Our motivation for a defender with stealthy moves is that it can not be assumed that every attacker can receive feedback from an APT. Some APTs can be resident on a isolated network (e.g. the \textit{Stuxnetworm}), meaning that there is no way to connect to the Internet. \\

@@

Even when the APT is launched to steal sensitive information the defender can set-up a honey pot, making the attacker believe that he is stealing sensitive information, but the information in the honeypot is all fake. Honeypots emulate services or creates multiple instances of real operating systems and can pretend to have sensitive information.  While the analysis in this paper is limited to immediate effect of the defender's moves, the case where the moves of the defender are non stealthy has already been investigated by Laszka \citep{MitigationNonTargeted}.

@@

\textbf{No feedback (non-adaptive)}\\
Non-adaptive strategies are chosen because of the assumption that both players will receive no feedback during the game. This is motivated by the fact that the identity of the attackers and their attack strategy is rarely known to the defenders. In the case of the attacker, if an attacker wants to have feedback, receiving feedback may compromise the desire to stay undetected. To be able to get feedback, the malware needs to make a connection with the attacker to provide this feedback. This may for example cause extra network traffic, which can be detected by the defender. \\

@@

\section{Formalization of the Periodic Game with Propagation Delay}
\label{ch2:periodicvirus}

@@

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.7]{Images/DefFlip.pdf}
\caption{Formalization of a FlipIt game with  propagation delay: A representation of a FlipIt game where both players are playing periodically. Every move or flip is indicated by a green or orange circle, respectively dark gray and light grey.  The defender is represented in green and plays with a period of $\delta_{D}$. The flip of the attacker is represented by a white circle, but because there is a delay d, the attacker only controls the resource after time d represented by an orange circle. The attacker plays with a period of $\delta_{A}$. The green and orange rectangles represent the amount of time the respective player is in control of the resource.}
\label{FlipItDelay}
\end{figure}

\begin{description}
\item $i$: Denotes the player. \textit{D} denotes the defender, and \textit{A} denotes the attacker which differs from the notation in \citep{FlipIt}, where the defender is denoted by the subscript \textit{0} and the attacker by the subscript \textit{1}.
\item $\delta_{i}$: The length of the interval between two consecutive moves of player \textit{i}. 
\item $\alpha_{i}$: The average flip rate of player \textit{i}, given by $\alpha_{i}=1/\delta_{i}$.
\item $k_{i}$: The cost of player \textit{i}'s moves.
\item $d$: The delay caused by the virus propagation.
\item $G_{i}(t)$: The total gain of player \textit{i}, which is the amount of time player \textit{i} is in control over the resource up to time \textit{t}.
\item $\gamma_{i}$: The average gain rate of player \textit{i}, defined as $G_{i}(t)/t$
\item $\beta_{i}$:  The average benefit rate up to time \textit{t}, defined as  $\beta_{i} = \gamma_{i} -k_{i} \alpha_{i} $.
\item $opt_{i}$: The optimum function for player \textit{i}. 
\end{description}

The adaptation of the FlipIt model starts from the assumption that, when an attacker attacks at time \textit{t}, he doesn't get immediate control over the resource, but he only gains control at time \textit{t + d}, with $d$ denoting the time needed to infect a sufficient number of (or all) nodes. If the defender flips the network before the period $d$ has elapsed (so, somewhere between $t$ and $t + d$), then the attacker will never gain full control over the resource. (See figure \ref{dt} at points 3 and 4). This implies that the mathematical formulas for gain and benefit need to be adapted to the fact that the attacker loses part of his benefit because of this delay. In the remainder of this paper, we will adapt the formalization of the FlipIt game using the delay variable $d$. \\ 
We adapt the same definition for players that play at the same time as in the original FlipIt game. The probability that this happens will be close to zero, but if it happens the moves cancel each other out and no change of control happens (see figure \ref{dt} point 3).\\
\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.7]{Images/Delayuitgelegd.pdf}
\caption{The first game is the basic FlipIt game. The second is the FlipIt game with a delay. During the first flip of the attacker, the defender moves after the delay (point 2), resulting in the attacker gaining control over the resource, until the defender flips. During the second flip of the attacker, the defender flips at time t+d, causing the defender to retain control over the resource before the attacker can gain control. During the third and final flip of the attacker, the defender flips during time t+d, causing the attacker to never gain control over the resource. }
\label{dt}
\end{figure}

%
We split the formalization in three cases. Similarly as in the original FlipIt game, there is the case where the defender plays at least as fast as the attacker, and the case where the attacker plays at least as fast as the defender. For each of these cases, the benefit formula of the basic case without delay is presented first, and subsequently the delay is introduced.  The third case is a special case where the period of the defender is smaller than the delay.\\

In the original model of FlipIt, the authors express the formulas in terms of $\alpha_{D}$ and $\alpha_{A}$. However, when introducing the delay, some formulas become much simpler when expressed in terms of $\delta_{D}$ and $\delta_{A}$. Therefore in the remainder of this paper, we will formulate the model using both $\alpha_{i}$ and $\delta_{i}$, depending on which variable gives the simplest representation of the formulas.

@@

This however results in an overestimation. 
%By simulation the game, it can be notices that the closer $\delta_{A}/\delta_{D}$ is equal to one, the better the approximation. If $\delta_{A}/\delta_{D} = 1$ the result is correct. 
The reason this formula overestimates the benefit of the attacker is that it assumes that the defender is always in control during the delay. However, if the attacker was in control in the previous interval, then he continues to be in control during the period of the delay, see figure \ref{fig:case2} situations 5 to 7. This means that the average benefit formulas for this case cannot be derived from one interval only; what happens in the previous interval must be taken into account. \\

@@

Consider a timespan $\delta_{A} + d$, representing the attacker's interval followed by the delay period in his next interval. If we assume that $\delta_{A}+d<\delta_{D}$, we can infer that the defender will never move twice during this timespan.
Because $d + \delta_{A} \leq \delta_{D}$ the next move of the defender in this second interval will never occur during the delay, meaning that the entire delay can be considered as an extra benefit resulting of a play in the previous interval. 
So, every time the defender plays, he will get an average gain of $\dfrac{\delta_{A}}{2}$ in the interval where he plays and in the next interval will always receive an extra gain of $d$, yielding a total average gain per interval of
$\dfrac{(d+\dfrac{\delta_{A}}{2})}{\delta_{A}}$

For the remainder of the analyses we consider two cases, Case 2.a and Case 2.b, depending on whether the delay is shorter or longer than the difference between the attacker's and the defender's period.  \\

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.7]{../../doc/template/Images/FlipIt2.pdf}
\caption{All possible cases for the attacker and the defender in Case 2.A where $d + \delta_{A} \leq \delta_{D}$. As can be seen in cases (1) to (4), the defender will have control during a period of \textit{d} over the resource in the next interval when the defender has flipped in the previous interval.}
\label{fig:case2}
\end{figure}

@@

It is crucial that $ \delta_{D}$ is at least as large as $d + \delta_{A}$. If not, the defender can move during the delay in the interval following the interval in which the defender already moved. This would result in an overlap between the average gain of $\dfrac{\delta_{A}}{2} +d$ and the delay. The above benefit formula would then include too much gain for the defender: the potential overlap during the delay would be counted twice. See figure \ref{countedtwice}.\\

@@

We calculated the benefit for three cases: when $\delta_{D}$ is smaller than $d$, when $\delta_{D}$ is smaller than $\delta_{A}$ and when $\delta_{D}$ is larger than $\delta_{A}$.
The benefit formulas of case 1 and case 2.b result in the same formula. Consequently, these two formulas can be brought together by adapting the border conditions. The first figure in figure \ref{Borders} shows all the cases and it can be seen that the border condition of case 1 and case 2.b can be brought together. This can be seen as the second figure in \ref{Borders}. \\

### 2015-08-19 doc/template/conclusion.tex
veranderingen opslagen

This paper presents an adaptation to the basic FlipIt game by \citep{FlipIt} to model an attacker with a delay.

\section{General results and conclusions}
Our FlipIt model with worm propagation delay showed us some interesting results. 
\begin{itemize}
\item When the defender plays faster than the delay, the attacker will either have a negative benefit or a benefit equal to zero if the flips do not cost anything. It is for the defender a target to be able to play at a rate smaller or equal to the delay.
\item If the defender can play with a cost equal to zero, the attacker will not play. The defender can play at any rate he wants, and the attacker is always disadvantaged by his delay.
\item If the cost of the defender is non-zero, then, depending on the ratio between it's cost and the delay, from a certain value for the speed of the attacker, the defender will not play. The same thing goes for the attacker. This result is similar to the results obtained for the original FlipIt game.
\end{itemize}

While the first two results are intuitively clear, in the third case, the mathematical analysis is important to determine the exact ratio's at which it is no longer beneficial for the defender to play. \\
In the next section we list a set of extensions that might be interesting for further research.
\section{Further work}

@@

As of today APTs become more and more extraordinary pieces of malicious code. There are APTs known to survive military-grade disk wiping and reformatting, and even after reformatting and reinstalling the operating system they are able to send sensitive data (Equation group \citep{Equation}). This means that even if you know that an APT is on your network, the actual practical ``flip'' has to exist and be known by the defender.  \\
Most often the best way to secure a system is to find the weakest link. This is mostly the employee. An effective way to counter this problem is to raise awareness about risks of infections amongst the employees.  Even in the presence of good security protection layers, spam filters, and firewalls, the opening of a phishing mail or use of an unknown USB stick by one of your employees may be suficient to infect a PC on the network, from which the virus can spread further. A system can however never be 100\% waterproof.  If an infection has occurred and the defender knows a countermeasure, the FlipIt game will help to determine the most effective pace at which countermeasures need to be taken.
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "thesis"
%%% End:

>>>>

This paper presented an adaptation to the basic FlipIt game by \citep{FlipIt} to model an attacker with a delay.

\section{General Results and Conclusions}
Our FlipIt model with worm propagation delay showed us some interesting results. 
\begin{itemize}
\item When the defender plays faster than the delay, the attacker will either have a negative benefit or a benefit equal to zero if the flips do not cost anything. It is for the defender a target to be able to play at a rate smaller or equal to the delay.
\item If the defender can play with a cost equal to zero, the attacker will not play. The defender can play at any rate he wants, and the attacker is always disadvantaged by his delay.
\item If the cost of the defender is non-zero, then, depending on the ratio between it's cost and the delay, from a certain value for the speed of the attacker, the defender will not play. The same thing goes for the attacker. This result is similar to the results obtained for the original FlipIt game.
\end{itemize}

While the first two results are intuitively clear, in the third case, the mathematical analysis is important to determine the exact ratio's at which it is no longer beneficial for the defender to play. \\
In the next section we list a set of extensions that might be interesting for further research.
\section{Further Work}

@@

As of today APTs become more and more extraordinary pieces of malicious code. There are APTs known to survive military-grade disk wiping and reformatting, and even after reformatting and reinstalling the operating system they are able to send sensitive data (Equation group \citep{Equation}). This means that even if you know that an APT is on your network, the actual practical ``flip'' has to exist and be known by the defender.  \\
Most often the best way to secure a system is to find the weakest link. This is mostly the employee. An effective way to counter this problem is to raise awareness about risks of infections amongst the employees.  Even in the presence of good security protection layers, spam filters, and firewalls, the opening of a phishing mail or use of an unknown USB stick by one of your employees may be sufficient to infect a PC on the network, from which the virus can spread further. A system can however never be 100\% waterproof.  If an infection has occurred and the defender knows a countermeasure, the FlipIt game will help to determine the most effective pace at which countermeasures need to be taken.
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "thesis"
%%% End:

### 2015-08-19 doc/template/nash.tex
veranderingen opslagen

\chapter{Optimal defence and attack strategies}
\label{chapter:Nash}
%\documentclass[10pt]{article}
%\begin{document}

@@

\section{Determining the piecewise functions $opt_{D}(\delta_{A})$}

@@

\section{Best responses of $\delta_{D}$}
The optimum functions will be piecewise functions. We distinguish six cases for different values of $\delta_{A}$ depending on the values of $k_{D}$ and $d$. 
%We point out that $\delta_{A}$ and $\delta_{D}$ are positive rates. 
Figure XXX shows on the left how the three cases can be combined in a single continuous function (shown as the thick line). On the right, the derivative function indicates at which points the benefit will change. It is interesting to note that the derivative is also continuous, meaning that the benefit function is smooth and has no rough edges or corners. This implies that there are no sudden changes in benefit for small changes of period.

@@

 \begin{displaymath}
  opt_{D}(\delta_{A}) = \left\{
     \begin{array}{lr}
     \left[0,d\right] & \delta_{A} =0 ~~\& ~~k_{D}=0 \\
     \left[0,d\right] & k_{D}=0\\
     d & \delta_{A} =0 ~~ \& k_{D} \leq d\\
          \infty , & \delta_{A} < 2(k_{D} - d)\\
      \left[ \sqrt{2k_{D}\delta_{A} + d^{2}},\infty\right[ , & \delta_{A} = 2(k_{D} - d) \\
      \sqrt{2k_{D}\delta_{A} + d^{2}}, & \delta_{A} > 2(k_{D} - d)
     \end{array}
   \right.
\end{displaymath}
%*****************************************************************
%
% optimum functies voor beta A
%
%*********************************************************************
\section{Determining the piecewise functions $opt_{A}(\delta_{D})$}
%To start with we only consider the case where $d < \delta_{D}$, because if $d > \delta_{D}$ the benefit of the defender \todo{nakijken, def of att} is always 1. \\
To determine the optimal strategy of the attacker we also need to determine $opt_{A}(\delta_{D})$ by computing the derivative of $\beta_{A}(\delta_{D},\delta_{A})$ for a fixed $\delta_{D}$. We consider the three cases of the piecewise function of $\beta_{A}$: \\

@@

The roots of this quadratic equation are $\delta_{D}=d+k_{A}\pm \sqrt{2dk_{A}+k_{A}^{2}}$. Because for this case $d\leq \delta_{D}$, we only look at root $\delta_{D}=d+k_{A} + \sqrt{2dk_{A}+k_{A}^{2}}$. $\sqrt{2dk_{A}+k_{A}^{2}}$ is bigger than $k_{A}$ so if we subtract it from $d+k_{A}$, we are in the part where $delta_{D}$ is smaller than d. \\
It follows that $\beta_{A}(\delta_{D},\delta_{A})$ is increasing and non-positive if $\delta_{D}> d+k_{A} + \sqrt{2dk_{A}+k_{A}^{2}}$ and decreasing and positive if $\delta_{D} < d+k_{A} + \sqrt{2dk_{A}+k_{A}^{2}}$  \\

\section{Best responses of $\delta_{A}$}
The optimum function of the attacker is found in the same way as the optimum function of the defender. The derivatives of each piece of the piecewise benefit function of the attacker is taken. From these derivatives the best responses are derived. \\
Case A is an edge case and will be addressed in the paragraph about the edge cases.
%The optimum functions will be piecewise functions. We distinguish three cases for different values of $\delta_{D}$ regarding $d$ and $k_{A}$. 
%
%
%For this term $\dfrac{(\delta_{D}-d)^{2}}{2k_{A}} $ , $d$ has to be bigger than  $\delta_{D}$ because the cost $\delta_{D}$ cannot be negative. This was an assumption that was already made, because the benefit of the defender will always be 1 if $d$ is bigger than  $\delta_{D}$.

@@

\begin{figure}[hbtp]
\centering
\includegraphics[scale=1]{Images/case1A.pdf}
\caption{ Illustration of the best response functions. The left functions are the piecewise benefit function of the attacker for a certain values of $k_{A},d$ and $\delta_{D}$. The right functions are the derivatives of the benefit functions on the left. The best responses are the values where the function intersects with the x-as. (A): $\delta_{D} > d+k_{A} + \sqrt{2dk_{A}+k_{A}^{2}}$, (B): $\delta_{D} = d+k_{A} + \sqrt{2dk_{A}+k_{A}^{2}}$, (C): $\delta_{D} < d+k_{A} + \sqrt{2dk_{A}+k_{A}^{2}}$}
\label{case1A}
\end{figure}

@@

 \begin{displaymath}
  opt_{A}(\delta_{D}) = \left\{
     \begin{array}{lr}
     \infty & \delta_{D} = 0 \\
     \left[0,\infty\right] & \delta_{D} \leq d ~~\& ~~k_{A}=0 \\
          \left[0,\delta_{D} - d\right] & \delta_{D} > d ~~\& ~~k_{A}=0 \\
                 \infty & \delta_{D} < \dfrac{(\delta_{D}-d)^{2}}{2k_{A}} \\
       \left[ \sqrt{d k_{A}\delta_{D}}, \infty\right],  & \delta_{D} = \dfrac{(\delta_{D}-d)^{2}}{2k_{A}} \\
       \sqrt{d k_{A}\delta_{D}}, & \delta_{D} > \dfrac{(\delta_{D}-d)^{2}}{2k_{A}}
     \end{array}
   \right.
\end{displaymath}
\\

@@

The piecewise functions $opt_{D}$ and $opt_{A}$ give some interesting results. \todo{resultaten nog toevoegen, zelfde als in de andere conclusie}

The Nash Equilibria can be found as the intersection points of the piecewise functions $opt_{A}(\delta_{D})$ and $opt_{D}(\delta_{A})$. For this we have to compare the function in terms of the relationship of the players move cost. We distinguish three cases: $k_{A} < k_{D} , ~k_{A} > k_{D} $ and $k_{A} = k_{D}$.

>>>>

\chapter{Optimal Defence and Attack Strategies}
\label{chapter:Nash}
%\documentclass[10pt]{article}
%\begin{document}

@@

\section{Determining the Piecewise Functions $opt_{D}(\delta_{A})$}

@@

\subsection{Best Responses of $\delta_{D}$}
The optimum functions will be piecewise functions. We distinguish six cases for different values of $\delta_{A}$ depending on the values of $k_{D}$ and $d$. 
%We point out that $\delta_{A}$ and $\delta_{D}$ are positive rates. 
Figure XXX shows on the left how the three cases can be combined in a single continuous function (shown as the thick line). On the right, the derivative function indicates at which points the benefit will change. It is interesting to note that the derivative is also continuous, meaning that the benefit function is smooth and has no rough edges or corners. This implies that there are no sudden changes in benefit for small changes of period.

@@

 \begin{displaymath}
  opt_{D}(\delta_{A}) = \left\{
     \begin{array}{lr}
     \left[0,d\right] & \delta_{A} =0 ~~\& ~~k_{D}=0 \\
     \left[0,d\right] & k_{D}=0\\
     d & \delta_{A} =0 ~~ \& k_{D} \leq d\\
          \infty , & \delta_{A} < 2(k_{D} - d)\\
      \left[ \sqrt{2k_{D}\delta_{A} + d^{2}},\infty\right[ , & \delta_{A} = 2(k_{D} - d) \\
      \sqrt{2k_{D}\delta_{A} + d^{2}}, & \delta_{A} > 2(k_{D} - d)
     \end{array}
   \right.
\end{displaymath}
%*****************************************************************
%
% optimum functies voor beta A
%
%*********************************************************************
\section{Determining the Piecewise Functions $opt_{A}(\delta_{D})$}
%To start with we only consider the case where $d < \delta_{D}$, because if $d > \delta_{D}$ the benefit of the defender \todo{nakijken, def of att} is always 1. \\
To determine the optimal strategy of the attacker we also need to determine $opt_{A}(\delta_{D})$ by computing the derivative of $\beta_{A}(\delta_{D},\delta_{A})$ for a fixed $\delta_{D}$. We consider the three cases of the piecewise function of $\beta_{A}$: \\

@@

The roots of this quadratic equation are $\delta_{D}=d+k_{A}\pm \sqrt{2dk_{A}+k_{A}^{2}}$. Because for this case $d\leq \delta_{D}$, we only look at root $\delta_{D}=d+k_{A} + \sqrt{2dk_{A}+k_{A}^{2}}$. $\sqrt{2dk_{A}+k_{A}^{2}}$ is bigger than $k_{A}$ so if we subtract it from $d+k_{A}$, we are in the part where $delta_{D}$ is smaller than d. \\
It follows that $\beta_{A}(\delta_{D},\delta_{A})$ is increasing and non-positive if $\delta_{D}> d+k_{A} + \sqrt{2dk_{A}+k_{A}^{2}}$ and decreasing and positive if $\delta_{D} < d+k_{A} + \sqrt{2dk_{A}+k_{A}^{2}}$. \\

\subsection{Best Responses of $\delta_{A}$}
The optimum function of the attacker is found in the same way as the optimum function of the defender. The derivatives of each piece of the piecewise benefit function of the attacker is taken. From these derivatives the best responses are derived. \\
Case A is an edge case and will be addressed in the paragraph about the edge cases.
%The optimum functions will be piecewise functions. We distinguish three cases for different values of $\delta_{D}$ regarding $d$ and $k_{A}$. 
%
%
%For this term $\dfrac{(\delta_{D}-d)^{2}}{2k_{A}} $ , $d$ has to be bigger than  $\delta_{D}$ because the cost $\delta_{D}$ cannot be negative. This was an assumption that was already made, because the benefit of the defender will always be 1 if $d$ is bigger than  $\delta_{D}$.

@@

\begin{figure}[hbtp]
\centering
\includegraphics[scale=1]{Images/case1A.pdf}
\caption{ Illustration of the best response functions. The left functions are the piecewise benefit function of the attacker for a certain values of $k_{A},d$ and $\delta_{D}$. The right functions are the derivatives of the benefit functions on the left. The best responses are the values where the function intersects with the x-as. (A): $\delta_{D} > d+k_{A} + \sqrt{2dk_{A}+k_{A}^{2}}$, (B): $\delta_{D} = d+k_{A} + \sqrt{2dk_{A}+k_{A}^{2}}$, (C): $\delta_{D} < d+k_{A} + \sqrt{2dk_{A}+k_{A}^{2}}$}.
\label{case1A}
\end{figure}

@@

 \begin{displaymath}
  opt_{A}(\delta_{D}) = \left\{
     \begin{array}{lr}
     \infty & \delta_{D} = 0 \\
     \left[0,\infty\right] & \delta_{D} \leq d ~~\& ~~k_{A}=0 \\
          \left[0,\delta_{D} - d\right] & \delta_{D} > d ~~\& ~~k_{A}=0 \\
            \infty & \delta_{D} < d+k_{A} + \sqrt{2dk_{A}+k_{A}^{2}} \\
       \left[ \delta_{D}-d, \infty\right],  & \delta_{D} = d+k_{A} + \sqrt{2dk_{A}+k_{A}^{2}} \\
    	\delta_{D}-d, & \delta_{D} > d+k_{A} + \sqrt{2dk_{A}+k_{A}^{2}}
     \end{array}
   \right.
\end{displaymath}
\\

@@

The piecewise functions $opt_{D}$ and $opt_{A}$ give some interesting results.

\begin{itemize}
\item When the defender plays faster than the delay, the attacker will either have a negative benefit or a benefit equal to zero if the flips do not cost anything. It is for the defender a target to be able to play at a rate smaller or equal to the delay.
\item If the defender can play with a cost equal to zero, the attacker will not play. The defender can play at any rate he wants, and the attacker is always disadvantaged by his delay.
\item If the cost of the defender is non-zero, then, depending on the ratio between it's cost and the delay, from a certain value for the speed of the attacker, the defender will not play. The same thing goes for the attacker. This result is similar to the results obtained for the original FlipIt game.
\end{itemize}

The Nash Equilibria can be found as the intersection points of the piecewise functions $opt_{A}(\delta_{D})$ and $opt_{D}(\delta_{A})$. For this we have to compare the function in terms of the relationship of the players move cost. %We distinguish three cases: $k_{A} < k_{D} , ~k_{A} > k_{D} $ and $k_{A} = k_{D}$.
